BFS search in miniKanren

### 2019-03-06 Paper/paper.tex
update

%%% NOTE %%%
%
% - plan paper writing
%   
%   * Abstract
%   * send to Dan
%   * Core Content
%     * how stream is implemented in TRS2's miniKanren
%     * how to do BFS search
%
% - when is the deadline
%
%   last year submission deadline July 23, 2018
%
%%%%%%%%%%%%

@@

For the above \texttt{run}, both search strategies produces answers in increasing order of costs, i.e. both of them are \emph{cost-respecting}. In more complicated cases, however, interleaving DFS does not always produces answers in cost-repecting order. For instance, with iDFS the \texttt{run} in Fig.~\ref{conde-repeato-iDFS} produces answers in a seemingly random order. In contrast, the same run with BFS produces answers in an expected order (Fig.~\ref{conde-repeato-BFS}).

@@

Streams are cost respective when they are initially constructed by \texttt{==}. However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}), a composer of stream, can break cost respectiveness. when its first argument, \texttt{s-inf} is infinite. The resulting mature part contains only the mature part of \texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature part -- the newly constructed thunk.

@@

The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) restores cost-respectiveness by combining the mature parts in the fashion of \texttt{append}. \texttt{append-inf} calls its helper immediately, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is the \texttt{s-inf} in the driver. Two streams are swapped in the third \texttt{cond} clause, where \texttt{s?} is also changed accordingly.

@@

The goal is to express BFS explicitly with queue, so that we don’t have to generate all answers of the same cost at once.

>>>>

%%% NOTE %%%
%
% - deadline?
%
%   last year submission deadline May 15, 2018
%
%%%%%%%%%%%%

@@

For the above \texttt{run}, both search strategies produces answers in increasing order of costs, i.e. both of them are \emph{cost-respecting}. In more complicated cases, however, interleaving DFS might not produce answers in cost-repecting order. For instance, with iDFS the \texttt{run} in Fig.~\ref{conde-repeato-iDFS} produces answers in a seemingly random order. In contrast, the same run with BFS produces answers in an expected order (Fig.~\ref{conde-repeato-BFS}).

@@

Streams are cost respective when they are initially constructed by \texttt{==}. However, the \texttt{mk-0} version of \texttt{append-inf} (Fig.~\ref{append-inf-0}) breaks cost respectiveness when its first argument, \texttt{s-inf}, is infinite. The resulting mature part contains only the mature part of \texttt{s-inf}. The whole \texttt{t-inf} goes to the resulting immature part.

@@

The \texttt{mk-1} version of \texttt{append-inf} (Fig.~\ref{append-inf-1}) restores cost-respectiveness by combining the mature parts in the fashion of \texttt{append}. This \texttt{append-inf} calls its helper immediately, with the first argument, \texttt{s?}, set to \texttt{\#{}t}, which means \texttt{s-inf} in the helper is the \texttt{s-inf} in the driver. Two streams are swapped in the third \texttt{cond} clause, where \texttt{s?} is also changed accordingly.

@@

The goal is to express BFS explicitly with queue, so that the system doesn't generate all answers of the same cost at once.
